Target Markdown

### 2022-05-12 _targets.Rmd
targets update

# load libraries for make
tar_option_set(packages = c("dplyr",
                            "tidyr",
                            "purrr",
                            "readr",
                            "quanteda",
                            "igraph",
                            "DiagrammeR",
                            "tibble",
                            "stringr",
                            "topicmodels",
                            "ggplot2",
                            "scales",
                            "ldatuning",
                            "quanteda",
                            "data.table",
                            "tidytext",
                            "tm"
                            ))

@@

    tar_target(one_author,
               read.csv2(here::here("data", "raw", "Binter_pubs.csv")),
               format = "qs"),
    tar_target(two_authors, read.csv2(here::here("data", "raw", "Binter_Kvapilova_pubs.csv")),
               format = "qs")

@@

   tar_target(topic_model, 
              make_topic_model(two_authors),
               format = "qs")

>>>>

# load libraries for make
tar_option_set(packages = c("dplyr",
                            "tidyr",
                            "purrr",
                            "readr",
                            "quanteda",
                            "igraph",
                            "DiagrammeR",
                            "tibble",
                            "stringr",
                            "topicmodels",
                            "ggplot2",
                            "scales",
                            "ldatuning",
                            "quanteda",
                            "data.table",
                            "tidytext",
                            "tm",
                            "httr",
                            "rjson",
                            "keyring",
                            "RSQLite",
                            "DBI"
                            ))

@@

    # tar_target(one_author,
    #           read.csv2(here::here("data", "raw",    #"Binter_pubs.csv")),
 #              format = "qs"),
      tar_target(ids, read.csv2(here::here("data", "raw", "supervisors.csv")),
              format = "qs"),
    tar_target(db_path,
           here::here("data", "raw", "czech_sci_db.sqlite")),
    tar_target(all_pubs,
           get_all_pubs(db_path, ids), 
              format = "qs")

   tar_target(topic_model, 
              make_topic_model(all_pubs),
               format = "qs")

@@
